% Resume content rendered with YAAC: Another Awesome CV.
\documentclass[localFont,alternative,10pt,compact]{yaac-another-awesome-cv}

\name{Vladimir}{Kim}
\tagline{Platform Engineer | Site Reliability Engineer | Backend Developer}
\socialinfo{
  \linkedin{vladimir-kim-7b20a6223}
  \github{kvladsrc}\\
  \smartphone{+48 451 633 718}
  \email{v.a.kim1988@gmail.com}\\
  \address{Poland}
}

\begin{document}

\makecvheader

\sectionTitle{Professional Summary}{\faUser}

\par{
Platform engineer with 10+ years of experience building and operating
production infrastructure. Strong in Go services, Kubernetes and OpenShift
platforms, CI/CD, observability, and cloud automation on GCP. Comfortable
moving between backend development and SRE work: designing reliable systems,
improving delivery pipelines, and keeping complex platforms understandable.
}

\sectionTitle{Target Positions}{\faBullseye}

\begin{keywords}
  \keywordsentry{}{Platform Engineer / Infrastructure Engineer}
  \keywordsentry{}{Site Reliability Engineer (SRE)}
  \keywordsentry{}{DevOps Engineer}
  \keywordsentry{}{Backend Developer (Go)}
\end{keywords}

\sectionTitle{Technical Skills}{\faTasks}

\begin{keywords}
  \keywordsentry{Programming}{Proficient in Go and its ecosystem; experience with Python and C\texttt{++}}
  \keywordsentry{Linux and operations}{Bash, coreutils, Ansible, RHEL, NixOS, Debian}
  \keywordsentry{Containers and platforms}{OpenShift, Kubernetes, OCI containers, Docker, cloud-native platform operations}
  \keywordsentry{Backend and APIs}{DRF, gRPC, Protobuf}
  \keywordsentry{CI/CD and GitOps}{Jenkins, Zuul CI, ArgoCD, FluxCD, Bazel, Gerrit, Cloud Build}
  \keywordsentry{Cloud and observability}{GCP, Terraform, Prometheus/Thanos, Alertmanager, Grafana, ELK, performance troubleshooting}
\end{keywords}

\sectionTitle{Work Experience}{\faSuitcase}

\begin{experiences}
  \experience
    {Present}
    {System Engineer}
    {EPAM Systems}
    {Poland}
    {Dec 2022}
    {
      \begin{itemize}
        \item Develop Go microservices with a focus on reliability, maintainability, gRPC APIs, and test coverage.
        \item Manage build systems and cloud resources across large engineering projects.
        \item Improve infrastructure automation and developer workflows around Bazel, Gerrit, Terraform, Cloud Build, and GCP.
      \end{itemize}
    }
    {Bazel, Gerrit, Terraform, Cloud Build, GCP, Go, Protobuf, gRPC}

  \emptySeparator

  \experience
    {Oct 2022}
    {DevOps Engineer}
    {Sberbank, CIB}
    {Kazakhstan}
    {May 2021}
    {
      \begin{itemize}
        \item Operated Linux and OpenShift infrastructure for containerized services.
        \item Built observability flows across metrics, logs, dashboards, and alerting.
        \item Led GitOps and platform delivery initiatives using Helm, ArgoCD, Jenkins, and Ansible.
      \end{itemize}
    }
    {OpenShift, Helm/Helmfile, ArgoCD, Jenkins, Ansible, Kafka, ELK, Prometheus/Thanos, Alertmanager, Grafana, RHEL}

  \emptySeparator

  \experience
    {May 2021}
    {Programmer / System Administrator}
    {Polpharma, SA}
    {}
    {Dec 2014}
    {
      \begin{itemize}
        \item Built internal business applications and backend APIs with Python.
        \item Administered Linux servers, load balancing, monitoring, and containerized deployments.
        \item Maintained SAP ERP and Oracle database environments, including availability and performance work.
        \item Supported data processing pipelines using Hadoop and ETL tooling.
      \end{itemize}
    }
    {Docker Swarm, Python, HAProxy, Nginx, Ansible, Hadoop, Oracle RDBMS, SAP ERP}

  \emptySeparator

  \experience
    {Oct 2014}
    {Developer}
    {openerp.kz, Llp}
    {Kazakhstan}
    {Nov 2012}
    {
      \begin{itemize}
        \item Developed backend services using Python web and asynchronous frameworks.
        \item Implemented embedded Linux integrations on Raspberry Pi with peripheral devices.
      \end{itemize}
    }
    {Twisted, asyncio, C, Raspberry Pi, Linux}
\end{experiences}

\end{document}
